Kepler and the Behemoth: Three Mini-Neptunes in a 40 Million Year Old Association

### 2022-04-29 papers/ms.tex
update ms

%
% KOI match numbers from calc_CepHer_group_numbers.py
%
Our fourth and final step was to cross-match the candidate Cep-Her
member list against all known Kepler Objects of Interest.  We used the
Cumulative KOI table from the NASA Exoplanet Archive from 27 March
2022, and also compared against the \texttt{q1\_q17\_dr25} table
\citep{thompson_planetary_2018}.  From the candidate members with
weights exceeding 0.02, this yielded 11 known false positives, 6
``confirmed'' planets, and 8 ``candidate'' planets.  Inspection of the
Kepler data validation summaries and Robovetter classifications for
these objects showed whether they were potentially consistent with
being {\it i)} planets, and {\it ii)} $\lesssim 10^8$ years old, based
on the presence of rotational modulation at the expected period and
amplitude \citep[{e.g.},][Figure~9]{rebull_rotation_2020}.  Four
objects remained after this inspection: Kepler-1627, Kepler-1643,
KOI-7368, and KOI-7913.
%\footnote{These figures
%yield an estimate of the size of Cep-Her: if our 4/14
%matches represent the true positive rate, then
%multiplying by the number of stars above our weight threshold
%(12{,}436) yields $\approx$3{,}500 stars in the complex.  
%This might however be an under-count,
%since Kepler observed sparse 
%regions of the complex, which are expected to have higher
%contamination rates (Figure~\ref{fig:XYZvtang}, top panel).}

@@

Figure~\ref{fig:age} also shows that most RSG-5 and CH-2 members
overlap with the $\delta$~Lyr cluster, and that the groups are
therefore roughly the same age.  To quantify this, we use the method
introduced by \citet[][their Section~6.3]{gagne_mutau_2020}.  The idea
is to fit the pre-main-sequence loci of a set of reference clusters,
and to then model the locus of the target cluster as a linear
combination of these reference cluster loci.  For our reference
clusters, we used UCL, IC\,2602, and the Pleiades, with the
memberships reported by \citet{Damiani2019} and
\cite{CantatGaudin2018a} respectively.  We adopted ages of 16\,Myr for
UCL \citep{pecaut_star_2016}, 38\,Myr for IC\,2602
\citep{david_ages_2015,randich_gaiaeso_2018}
%\footnote{ Ages for
%IC\,2602 vary from 40 to 46\,Myr based on lithium-depletion-boundary
%(LDB) measurements \citep{dobbie_ic_2010,randich_gaiaeso_2018}, and
%from 30 to 46\,Myr based on isochronal analyses
%\citep{stauffer_rotational_1997,david_ages_2015,bossini_age_2019}.},
and 112\,Myr for the Pleiades \citep{dahm_2015}.  These assumptions
and the subsequent processing steps taken to exclude field stars and
binaries were identical to those described in
\citet{bouma_kep1627_2022}.  The mean and uncertainty of the resulting
age posterior are $46^{+9}_{-7}$\,Myr for RSG-5, and
$36^{+10}_{-8}$\,Myr for CH-2.  For comparison, this procedure yields
an age for the $\delta$~Lyr cluster of $38^{+6}_{-5}$\,Myr.  The
older isochronal age of RSG-5 is consistent with its location
relative to the $\delta$~Lyr cluster in the upper left panel of
Figure~\ref{fig:age}.

@@

\paragraph{High-Resolution Imaging}
We acquired adaptive optics imaging of Kepler-1643 on the night of
2019 June 28 using the NIRC2 imager on Keck-II.  Using the narrow
camera (FOV = 10.2\arcsec), we obtained 4 images in the $K'$ filter
($\lambda = 2.12\,\mu$m) with a total exposure time of 320\,s. We
analyzed these data following \citet{kraus_impact_2016}, and
determined the detection limits to visual companions by analyzing the
residuals after subtracting an empirical PSF template.  This procedure
yielded contrast limits of $\Delta K' = 4.1$ mag at $\rho = 150$ mas,
$\Delta K' = 5.8$ mag at $\rho = 300$ mas, and $\Delta K' = 8.3$ mag
at $\rho > 1000$ mas.

@@

\paragraph{Binarity}
KOI-7913 is a binary.  The north-west primary is
$\approx$0.5 magnitudes brighter than the south-east secondary in
optical passbands.  The two stars are separated in Gaia EDR3 by
$3\farcs5$ on-sky, and have parallaxes consistent within $1$-$\sigma$
(with an average $\varpi=3.66 \pm 0.01$\,mas).  The apparent on-sky
separation is $959 \pm 2$ au.  The Gaia EDR3 proper motions are also
nearly identical.  Since two stars were resolved in the Kepler Input
Catalog and are roughly one Kepler pixel apart, an accurate crowding
metric has already been applied in the NASA Ames data products to
correct the mean flux level \citep{2017ksci.rept....6M}.  This is
important for deriving accurate transit depths.

@@

The theoretical expectation is that mini-Neptunes with sizes of 2 to
3\,$R_\oplus$ should be common at ages of $10^7$ to $10^8$ years.
This expectation is tied to inferences about the initial distributions
of planetary core mass, core composition, and atmospheric mass
fraction \citep{owen_evaporation_2017}.  The Kelvin-Helmholtz cooling
timescale, which is tied to the entropy of the planetary interior
shortly after
disk dispersal, also plays a significant role
\citep{owen_constraining_2020}.  As an example,
\citet{rogers_unveiling_2021} predicted that given a core-mass
distribution peaked at $\approx$$4$\,$M_\oplus$, an ice-poor rock/iron
core composition, and a typical H/He mass fraction of $\approx$4\%,
there should be a maximum in planet occurrence at 2 to 3\,$R_\oplus$
at times between 10 and 100\,Myr.  The models
advanced by \citet{gupta_signatures_2020} and
\citet{lee_primordial_2021} agree; their differences lie in the mechanism
for producing the radius valley. 
% If the radius valley is
% primordial and created by gas accretion physics, then super-Earths
% ($<$$1.8$\,$R_\oplus$) would be common as early as $10^7$ years
% \citep{lee_primordial_2021}.   The photoevaporation-driven models more
% often quote $10^8$ year timescales for production of
% atmosphere-stripped super-Earths, while the models with the mass-loss
% driven by a slow escape of heat from the core predict longer
% $\sim$$10^9$ year timescales (but see \citealt{king_2021}).

@@

A number of worthy photometric projects also seem possible given the
new understanding of Cep-Her.  One is asteroseismology of the
$\delta$~Sct stars, using either TESS or Kepler data
\citep{bedding_very_2020}.  For cases in which the modes are resolved,
this might yield age or metallicity estimates for the subgroups
independent of other methods.  Other projects could include
searches of the Kepler light curves for exocomets
\citep{zieba_transiting_2019}, and for missed planets around the most
rapid rotators.

>>>>

%
% KOI match numbers from calc_CepHer_group_numbers.py
%
Our fourth and final step was to cross-match the candidate Cep-Her
member list against all known Kepler Objects of Interest.  We used the
Cumulative KOI table from the NASA Exoplanet Archive from 27 March
2022, and also compared against the \texttt{q1\_q17\_dr25} table
\citep{thompson_planetary_2018}.  From the candidate members with
weights exceeding 0.02, this yielded 11 known false positives, 6
``confirmed'' planets, and 8 ``candidate'' planets.  Inspection of the
Kepler data validation summaries and Robovetter classifications for
these objects showed whether they were potentially consistent with
being {\it i)} planets, and {\it ii)} $\lesssim 10^8$ years old, based
on the presence of rotational modulation at the expected period and
amplitude \citep[{e.g.},][Figure~9]{rebull_rotation_2020}.  Four
objects remained after this inspection: Kepler-1627, Kepler-1643,
KOI-7368, and KOI-7913.

@@

Figure~\ref{fig:age} also shows that most RSG-5 and CH-2 members
overlap with the $\delta$~Lyr cluster, and that the groups are
therefore roughly the same age.  To quantify this, we use the method
introduced by \citet[][their Section~6.3]{gagne_mutau_2020}.  The idea
is to fit the pre-main-sequence loci of a set of reference clusters,
and to then model the locus of the target cluster as a linear
combination of these reference cluster loci.  For our reference
clusters, we used UCL, IC\,2602, and the Pleiades, with the
memberships reported by \citet{Damiani2019} and
\cite{CantatGaudin2018a} respectively.  We adopted ages of 16\,Myr for
UCL \citep{pecaut_star_2016}, 38\,Myr for IC\,2602
\citep{david_ages_2015,randich_gaiaeso_2018} and 112\,Myr for the
Pleiades \citep{dahm_2015}.  These assumptions and the subsequent
processing steps taken to exclude field stars and binaries were
identical to those described in \citet{bouma_kep1627_2022}.  The mean
and uncertainty of the resulting age posterior are $46^{+9}_{-7}$\,Myr
for RSG-5, and $36^{+10}_{-8}$\,Myr for CH-2.  For comparison, this
procedure yields an age for the $\delta$~Lyr cluster of
$38^{+6}_{-5}$\,Myr.  The older isochronal age of RSG-5 is consistent
with its location relative to the $\delta$~Lyr cluster in the upper
left panel of Figure~\ref{fig:age}.

@@

\paragraph{High-Resolution Imaging}
We acquired adaptive optics imaging of Kepler-1643 on the night of
2019 June 28 using the NIRC2 imager on Keck-II.  Using the narrow
camera (FOV = 10.2\arcsec), we obtained 4 images in the $K'$ filter
($\lambda = 2.12\,\mu$m) with a total exposure time of 320\,s. 
The images did not show any additional visual companions.
We analyzed the data following \citet{kraus_impact_2016}, and
determined the detection limits by analyzing the residuals after
subtracting an empirical PSF template.  This procedure yielded
contrast limits of $\Delta K' = 4.1$ mag at $\rho = 150$ mas, $\Delta
K' = 5.8$ mag at $\rho = 300$ mas, and $\Delta K' = 8.3$ mag
at $\rho > 1000$ mas.

@@

\paragraph{Binarity}
KOI-7913 is a binary.  The north-west primary is
$\approx$0.5 magnitudes brighter than the south-east secondary in
optical passbands.  The two stars are separated in Gaia EDR3 by
$3\farcs5$ on-sky, and have parallaxes consistent within $1$-$\sigma$
(with an average $\varpi=3.66 \pm 0.01$\,mas).  The apparent on-sky
separation is $959 \pm 2$ au.  The Gaia EDR3 proper motions are also
very similar.  Since two stars were resolved in the Kepler Input
Catalog and are roughly one Kepler pixel apart, an accurate crowding
metric has already been applied in the NASA Ames data products to
correct the mean flux level \citep{2017ksci.rept....6M}.  This is
important for deriving accurate transit depths.

@@

The theoretical expectation is that mini-Neptunes with sizes of 2 to
3\,$R_\oplus$ should be common at ages of $10^7$ to $10^8$ years.
This expectation is tied to inferences about the initial distributions
of planetary core mass, core composition, and atmospheric mass
fraction \citep{owen_evaporation_2017}.  The Kelvin-Helmholtz cooling
timescale, which is tied to the entropy of the planetary interior
shortly after disk dispersal, also plays a significant role
\citep{owen_constraining_2020}.  As an example,
\citet{rogers_unveiling_2021} predicted that given a core-mass
distribution peaked at $\approx$$4$\,$M_\oplus$, an ice-poor rock/iron
core composition, and a typical H/He mass fraction of $\approx$4\%,
there should be a maximum in planet occurrence at 2 to 3\,$R_\oplus$
at times between 10 and 100\,Myr.  The models advanced by
\citet{gupta_signatures_2020} and \citet{lee_primordial_2021} agree;
their differences lie in the mechanism for producing the radius
valley.

@@

A number of worthy photometric projects also seem possible given the
new understanding of Cep-Her.  One is asteroseismology of the
$\delta$~Sct stars, using either TESS or Kepler data
\citep{bedding_very_2020}.  For cases in which the modes are resolved,
this might yield age or metallicity estimates for the subgroups
independent of other methods.  Other projects could include a more
comprehensive analysis of the stellar rotation periods,
searches of the Kepler light curves for exocomets
\citep{zieba_transiting_2019}, and searches for missed planets around
the most rapid rotators.
